\textbf{Emergency Service Location Optimization in a Multi-Zone County based on Population Distribution}

### 2013-11-16 LaTeX/paper.tex
Adding to results

We ran the greedy algorithm for $n=3$ and we got that ambulances should be placed in zones
2, 3, and 5. This arrangement has ambulances cover all of zones 2-6 and half (25000/50000) of
zone 1.

\subsubsection{$n=2$}
We ran the greedy algorithm for $n=2$ and we got that ambulances should be placed in zones
2 and 5. This arrangement has ambulances cover all of zones 2, 4-6, half (25000/50000) of
zone 1, and none of zone 3.

\subsubsection{$n=1$}
We ran the greedy algorithm for $n=1$ and we got that our ambulance should be placed in zone 5. This arrangement allows the single ambulance to cover all of zone 4-6.

>>>>

Figure 2 above shows every possible route between zones, with their respective weight, or in this case, the time necessary to travel from one zone to another. For example, traveling from Zone 1 to Zone 6 would take 16 minutes, and vice versa.

However, if you look at each of the routes, you see that some paths take longer than 8 minutes to travel. In this case, it would be impossible for an ambulance to make it from one zone to another in the necessary 8 minute time interval, and therefore, it would be impossible to save anyone along that route.

In order to combat this, we look at Figure 3, above, which has significantly fewer paths. By eliminating the paths that require a travel time of more than 8 minutes, we have effectively cut our search time significantly, and allows to intuitively see some features of the graph.

First and foremost, if you look at Zone 2, you see two paths going out to Zones 1 and 3, respectively. Because of the short travel time it takes to get to both of the zones, the reach of an ambulance coming out of Zone 5 is slightly larger, and you are more likely to save more people. Furthermore, the overall population density of the three zones (1+2+3) is large, weighing Zone 2 as one of the more important nodes on the graph. Therefore, intuitively, Zone 2 makes sense as a starting point.

In the same way, if you look at Zone 5, you see two other paths going outwards to Zone 4 and Zone 6, respectively. Because neither of these two zones is represented with placing an ambulance in Zone 2, it follows that another ambulance should be placed in Zone 5, therefore covering the bulk of the county.

Finally, if you look at Zone 3, you see that while though redundant, the overall population covered by having an ambulance stationed there is the next greatest. For that reason, it makes the most sense to place the third ambulance in Zone 3.

Intuitively then, just by looking at the graphs, it makes the most sense that Zones 2, 5, and 3 are the most likely in which to place the ambulances in order to reach the most people in 8 minutes. Therefore, it shouldn't be surprising that when we ran the greedy algorithm for $n=3$ we got that ambulances should be placed in zones
2, 5, and 3. When we matched this up with our population coverage math, we found that this arrangement has ambulances cover all of zones 2-6 and half (25000/50000) of zone 1, accounting for a majority of the county.

\subsubsection{$n=2$}
When we ran the greedy algorithm for $n=2$ we got that ambulances should be placed in zones
2 and 5, which also intuitively follows from the graph. This arrangement has ambulances cover all of zones 2, 4-6, half      (25000/50000) of zone 1, and none of zone 3.

\subsubsection{$n=1$}
Finally, when we ran the greedy algorithm for $n=1$ we found that our ambulance should be placed in zone 2. This arrangement allows the single ambulance to cover all of zone 1-3, which represents the highest population on the map.
